Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2017-12-12 paper/paper.Rmd
working on image characteristics

```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "The mosaic plots indicate the proportion of faces given the angle, or situation, that matched faces found manually. The stacked bar charts show the amount of faces captured at certain angles, or situation.\\label{fig:ICFigs}"}

@@

grid.arrange(plots1, plots2, nrow=2)

@@

>>>>

```{r ICFigs, fig.width = 8, fig.height = 8, fig.cap = "Relationships between court and face characteristics, and API detection, using mosaic plots: (a) Angle of face capture, (b) court situation, (c) angle of capture by background, and (d) situtation of capture by background. Most face captures occurred at a level angle, and this produces slightly better detection. Most situtation face captures are close up, but the detection rate is identical regardless of situation. Most level angles had the logo wall in the background, while most birds-eye had the court as background, as we would expect. Close ups were mostly against the logo wall.  \\label{fig:ICFigs}"}

@@

grid.arrange(plots2, plots1, nrow=2)

@@

There were several characteristics of the image recorded during manual tagging, as listed in Table \@ref(tab:Scene-Attributes-Table). This section examines the prevalence of these characteristics in the data collection.
